\LARGE \bf Sandhi: An open source alternative to LabVIEW

### 2014-01-19 paper.tex
Fixed Author names, ff=unix

\author{Albert Author$^{1}$ and Bernard D. Researcher$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Albert Author is with Faculty of Electrical Engineering, Mathematics and Computer Science,
     University of Twente, 7500 AE Enschede, The Netherlands
     {\tt\small albert.author@papercept.net}}%
\thanks{$^{2}$Bernard D. Researcheris with the Department of Electrical Engineering, Wright State University,
     Dayton, OH 45435, USA
     {\tt\small b.d.researcher@ieee.org}}%
}

@@

GNU Radio is an open source radio implementation which is used by the Electrical Engineering community for the purpose of digital signal processing. It has a rich module of device drivers and thereby supports a range of devices. GNURadio is very promising visual programming tool as it makes it very easy for the developer to abstract his code, and provides a very easy to use framework to the developer. On top of all these advantages it is open source and hence making it potentially very attractive alternative to control system enthusiasts, who use SIMULINK/ LabVIEW for doing rapid prototyping of control schemes.

@@

However, this may not be very helpful for control system engineers since lot of their flow graphs have closed loops and hardcoding the blocks to make it open loop is counter-intutive. Thus, a separate scheduler called GNU Radio Advanced Scheduler is being developed to incorporate closed loop flow graphs. It uses C++ libaries such as Theron(concurrency library), PMC(Polymorphic Message Container for C++ library) etcetra.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{csim.png}
	\caption{Continuous time simulation flow graph}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{dsim.png}
	\caption{Discrete time simulation flow graph}
	\label{overflow}
\end{figure}

@@

So far we've been able to solve the servo problem using Sandhi. The work on regulatory problem is under-way. The controller controls the plant as per the backward difference equation 
\begin{equation}
	\begin{split}
	u(t) =u(t-1) + K_c[e(t)-e(t-1)] +  {\frac{K_c T_s}{T_i}}e(t) + \\
	{\frac{K_c T_d}{T_s}}[e(t)-2e(t-1)+e(t-2)] 
	\end{split}
\end{equation}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{sbhs_sandhi.png}
	\caption{Set point tracking of SBHS in Sandhi}
	\label{overflow}
\end{figure}

@@

	\bibitem{c1} GNU Radio- The Free \& Open Software Radio Ecosystem- Blocks Coding guide in C++ and tutorials for writing Python Application http://gnuradio.org/redmine/projects/gnuradio/wiki/BlocksCodingGuide
	\bibitem{c2} Virtual Labs initiative http://en.wikipedia.org/wiki/Virtual\_Labs\_(India) 
	\bibitem{c3} Inderpreet Arora, Kannan M. Moudgalya, Kaushik Venkata, Victor Chakraborty, Rupak Rokade and Rakhi R., A Low Cost, Scalable, Virtual Control Laboratory, Santiago, Chile, IEEE Conference on Control and Automation.
	\bibitem{c4} Sciscipy: Scilab API for Python http://forge.scilab.org/index.php/p/sciscipy
	\bibitem{c5} Linux on Aakash tablet https://github.com/androportal/linux-on-aakash
	\bibitem{c6} GNU Radio Advanced Scheduler, developed by Josh Blum, Ettus Resarch, https://github.com/guruofquality/gras
	\bibitem{c7} GNU Radio Python blocks Writing python blocks https://github.com/aviralchandra/gr-py\_block
	\bibitem{c8} Jagdish Y. Patil, Balashish Dubey, Kannan M. Moudgalya, Rakesh Peter: GNURadio, Scilab, Xcos and COMEDI for Data Acquisition and Control: An Open Source Alternative to LabVIEW, Article, IIT Bombay, Mumbai 400076
	\bibitem{c9} Dictino Chaos1;*, Jes  ¿us Chac ¿on1, Jose Antonio Lopez-Orozco2 and Sebasti ¿an Dormido1 : Virtual and Remote Robotic Laboratory Using EJS, MATLAB and LabVIEW
	\bibitem{c10} Kannan M. Moudgalya. Digital Control. John Wiley and Sons, 2009
	\bibitem{c11} Scilab, open source software for numerical computation, www.scilab.org
\end{thebibliography}

>>>>

\author{\IEEEauthorblockN{Manoj Gudi\IEEEauthorrefmark{1},
			  Aviral Chandra\IEEEauthorrefmark{2},
		          Kannan M. Moudgalya\IEEEauthorrefmark{3}}

	\IEEEauthorblockA{\IEEEauthorrefmark{1}FOSSEE, IIT Bombay, Mumbai 400076\\
	manoj\_gudi@iitb.ac.in}
	\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Chemical Engineering, IIT Bombay, Mumbai 400076\\
	aviral\_chandra@iitb.ac.in}
	\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Chemical Engineering, IIT Bombay, Mumbai 400076\\
kannan@iitb.ac.in}}

@@

GNU Radio is an open source radio implementation which is used by the Electrical Engineering community for the purpose of digital signal processing. It has a rich module of device drivers and thereby supports a range of devices. GNU Radio is very promising visual programming tool as it makes it very easy for the developer to abstract his code, and provides a very easy to use framework to the developer. On top of all these advantages it is open source and hence making it potentially very attractive alternative to control system enthusiasts, who use SIMULINK/ LabVIEW for doing rapid prototyping of control schemes.

@@

However, this may not be very helpful for control engineers since most of the flow graphs are closed-loops. Implementing closed loop system through hard coding defeats the purpose of a visual programming editor.

Thus, a separate scheduler called GNU Radio Advanced Scheduler is being developed to incorporate closed loop flow graphs. It uses C++ libaries such as Theron(concurrency library), PMC(Polymorphic Message Container for C++ library) etcetra.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{csim_closed.png}
	\caption{Closed loop continuous time simulation flow graph}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{dsim_closed.png}
	\caption{Closed loop discrete time simulation flow graph}
	\label{overflow}
\end{figure}

@@

So far we've been able to solve the servo problem using Sandhi. The work on regulatory problem is under-way. The controller controls the plant as per the PID controller equation, implemented as the following backward difference equation-
\begin{equation}
	\begin{split}
	u(t) =u(t-1) + K_c[e(t)-e(t-1)] +  {\frac{K_c T_s}{T_i}}e(t) + \\
	{\frac{K_c T_d}{T_s}}[e(t)-2e(t-1)+e(t-2)] 
	\end{split}
\end{equation}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{sbhs_sandhi.png}
	\caption{Set point tracking of temperature of SBHS in Sandhi}
	\label{overflow}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{scope_plot.png}
	\caption{Real time plot illustrating set point trajectory versus time}
	\label{overflow}
\end{figure}

@@

	\bibitem{c1} GNU Radio- The Free \& Open Software Radio Ecosystem- Blocks Coding guide in C++ and tutorials for writing Python Application http://gnuradio.org/redmine/projects/gnuradio/wiki/BlocksCodingGuide
	\bibitem{c2} Virtual Labs initiative http://en.wikipedia.org/wiki/Virtual\_Labs\_(India) 
	\bibitem{c3} Inderpreet Arora, Kannan M. Moudgalya, Kaushik Venkata, Victor Chakraborty, Rupak Rokade and Rakhi R., A Low Cost, Scalable, Virtual Control Laboratory, Santiago, Chile, IEEE Conference on Control and Automation.
	\bibitem{c4} Sciscipy: Scilab API for Python http://forge.scilab.org/index.php/p/sciscipy
	\bibitem{c5} Linux on Aakash tablet https://github.com/androportal/linux-on-aakash
	\bibitem{c6} GNU Radio Advanced Scheduler, developed by Josh Blum, Ettus Resarch, https://github.com/guruofquality/gras
	\bibitem{c7} GNU Radio Python blocks Writing python blocks https://github.com/aviralchandra/gr-py\_block
	\bibitem{c8} Jagdish Y. Patil, Balashish Dubey, Kannan M. Moudgalya, Rakesh Peter: GNU Radio, Scilab, Xcos and COMEDI for Data Acquisition and Control: An Open Source Alternative to LabVIEW, Article, IIT Bombay, Mumbai 400076
	\bibitem{c9} Dictino Chaos1;*, Jes  ¿us Chac ¿on1, Jose Antonio Lopez-Orozco2 and Sebasti ¿an Dormido1 : Virtual and Remote Robotic Laboratory Using EJS, MATLAB and LabVIEW
	\bibitem{c10} Kannan M. Moudgalya. Digital Control. John Wiley and Sons, 2009
	\bibitem{c11} Scilab, open source software for numerical computation, www.scilab.org
\end{thebibliography}
